Titanic data set will be analyzed here by using random forest. Here the step by step:
1. Reading train and test data set
2. Filling the missing data with their median
3. Using random forest as predictive model
4. Writing csv dataframe for Kaggle submission

Setting working directory. May be different for every user.
```{r}
setwd("~/R/Titanic Data Analysis")
```

Calling random forest library
```{r}
library(randomForest)
```

reading the csv data
```{r}
train <- read.csv(file="https://raw.githubusercontent.com/imdwipayana/DATA/main/Data%20Titanic/train.csv", stringsAsFactors = FALSE, header = TRUE)
test <- read.csv(file="https://raw.githubusercontent.com/imdwipayana/DATA/main/Data%20Titanic/test.csv",stringsAsFactors = FALSE,header = TRUE)
```

Check the head and tail of data by using:
```{r}
head(train)
tail(train)
```
The next step, we filling the missing data by using the median
```{r}
median(train$Age)
```
The result is NA because there are some missing data in Age. We try to ignore them first.
```{r}
median(train$Age, na.rm = TRUE)
median(test$Age, na.rm = TRUE)
```

Calling the column title for each data
```{r}
names(train)
names(test)
```

There is no Survived column in test data, we create a new Column for test dataset and filling them with NA
```{r}
test$Survived <- NA
```

Checking the number of column for test data set
```{r}
ncol(test)
names(test)
```

Adding a new column for both train and test data set in purpose to label them either the member of train or test data set.
```{r}
train$divide <- TRUE
test$divide <- FALSE
```

Merge both data set to be one data set called all.data
```{r}
all.data <- rbind(train,test)
```

Looking for the divide column
```{r}
table(all.data$divide)
```

Testing for empty dataset
```{r}
table(all.data$Embarked)
```

Filling the empty data of Embarked with the majority ('S')
```{r}
all.data[all.data$Embarked=='','Embarked'] <- 'S'
```

Checking again the Embarked column
```{r}
table(all.data$Embarked)
```

Looking empty data on Age
```{r}
table(is.na(all.data$Age))
```

Calculate the median of full data set
```{r}
median.age <- median(all.data$Age, na.rm=TRUE)
```

Filling missing data on Age with its median
```{r}
all.data[is.na(all.data$Age),'Age'] <- median.age
```

Checking there is no remaining missing data on Age
```{r}
table(is.na(all.data$Age))
```

Calculate median of Fare
```{r}
median.fare <- median(all.data$Fare, na.rm=TRUE)
```

Filling the Fare missing data with median of Fare
```{r}
all.data[is.na(all.data$Fare), 'Fare'] <- median.fare
```

Checking Fare missing values
```{r}
table(is.na(all.data$Fare))
```

Create categorical factor using as.factor
```{r}
all.data$Pclass <- as.factor(all.data$Pclass)
all.data$Sex <- as.factor(all.data$Sex)
all.data$Embarked <- as.factor(all.data$Embarked)
```

Divide back the full data set into train and test data set
```{r}
train <- all.data[all.data$divide==TRUE,]
test <- all.data[all.data$divide==FALSE,]
```

Checking data type
```{r}
str(train)
```

Transform Survived column on train data set to be a factor
```{r}
train$Survived <- as.factor(train$Survived)
```

Predictive model using random forest
```{r}
survived.app <- "Survived ~ Pclass + Sex + Age + SibSp + Parch + Fare + Embarked"
survived.formula <- as.formula(survived.app)
model.titanic <- randomForest(formula=survived.formula, data=train, ntree=500, mtry=3, nodesize=0.01*nrow(test))
feature.app <- "Pclass + Sex + Age + SibSp + Parch + Fare + Embarked"
Survived <- predict(model.titanic, newdata = test)
```

Create data frame for Kaggle submission
```{r}
PassengerId <- test$PassengerId

result <- as.data.frame(PassengerId)
result$Survived <- Survived
```

Write data to csv file as Kaggle submission
```{r}
write.csv(result,file="Submission.csv", row.names=FALSE)
```
